Rule Synthesis for Rule-based Intrusion Detectors

### 2020-06-03 paper/paper.tex
rephrase optimization senttence

The algorithm also takes as input the range of the weights (between 0 and 1) 
and the max number of generations, which we set to 10 (higher values could 
potentially better results, but also would take more time). The weights are 
as follows $\langle{}0.280, 0.057, 0.043, 0.490\rangle$.

>>>>

The algorithm also takes as input the range of the weights (between 0 and 1) 
and the max number of generations, which we set to 10 (confirmation whether 
this number suffices remains to future work). The weights are 
as follows $\langle{}0.280, 0.057, 0.043, 0.490\rangle$.
